Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-07-24 sections/3algebras.tex
.

The second step is then showing that the functors constructed above are equivalences, which we summarize in the following results:
%
\begin{theorem}\label{thm:disk_alg=lcfa}
    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \lcfa_M (\catC)
    \end{equation}
    %
    between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$. Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$.
\end{theorem}
%
\begin{corollary}\label{cor:disk_alg=falg}
    The $\infty$-operad governing factorization algebras on a stratified manifold $M$ can be taken to be $\disk[r]_{/M}$,
    %
    \begin{equation}
        \alg{\disk[r]_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \falg_M (\catC).
    \end{equation}
\end{corollary}
%
The reason for the phrasing in these results is that, technically speaking, equivalence of the $\infty$-categories of algebras does not imply equivalence of the underlying operads. However since we only defined (locally constant) factorization algebras at the level of algebras and not on the level of $\infty$-operads, we can take the operadic definition as the basic one, and interpret the results as connecting this to the classical definition. The theorems that we present in this section are immensely helpful in relating factorization algebras to results in the area of disk algebras, which will be obvious throughout the rest of this work. One important example that we will see is in \Cref{ch:gluing_disk_alg}.

@@

    where we have fixed the notation $\iota: D \xhookrightarrow{} M$ and $e: N \xhookrightarrow{} M$, for the domains of these maps. We further establish the notation that for each isomorphism class of basics $[B]$, the fixed $D$ has $i_[B]$-many disks of type $[B]$. With this notation in hand, by the characterization of the maximal $\infty$-subgroupoid of $\disk_{/M}$ \cite[Lem.2.21]{aft_fhstrat} for example, we know that

@@

\begin{proof}
    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is a weak equivalence of $\infty$-operads between $\disk (\mathsf{D}_n^*)$ and $\mathbb{E}_n$, i.e.
    %
    \begin{equation}
        \alg{\disk (\mathsf{D}_n^*)} \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n}.
    \end{equation}
    %
    But this is just the fact that the $\disk_{/M}$ $\infty$-operad gives rise to $\mathbb{E}_n$-algebras from \cref{prop:framed_ndisk=En}.
\end{proof}

>>>>

The second step is then showing that the functors constructed above are equivalences, which we summarize in the following results:
%
\begin{theorem}\label{thm:disk_alg=lcfa}
    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \lcfa_M (\catC)
    \end{equation}
    %
    between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$. Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$.
\end{theorem}
%
\begin{corollary}\label{cor:disk_alg=falg}
    The $\infty$-operad governing factorization algebras on a stratified manifold $M$ can be taken to be $\disk[r]_{/M}$,
    %
    \begin{equation}
        \alg{\disk[r]_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \falg_M (\catC).
    \end{equation}
\end{corollary}
%
The reason for the phrasing in these results is that, technically speaking, equivalence of the $\infty$-categories of algebras does not imply equivalence of the underlying $\infty$-operads. However since we only defined (locally constant) factorization algebras at the level of algebras and not at the level of $\infty$-operads, we can take the operadic definition as the basic one, and interpret the results as connecting this to the classical definition. The theorems that we present in this section are immensely helpful in relating factorization algebras to results in the area of disk algebras, which will be obvious throughout the rest of this work. One important example that we will see is in \Cref{ch:gluing_disk_alg}.

@@

    where we have fixed the notation $\iota: D \xhookrightarrow{} M$ and $e: N \xhookrightarrow{} M$, for the domains of these maps. We further establish the notation that for each isomorphism class of basics $[B]$, the fixed $D$ has $i_{[B]}$-many disks of type $[B]$. With this notation in hand, by the characterization of the maximal $\infty$-subgroupoid of $\disk_{/M}$ \cite[Lem.2.21]{aft_fhstrat} for example, we know that

@@

\begin{proof}
    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is a weak equivalence of $\infty$-operads between $\disk (\mathsf{D}_n^*)$ and $\mathbb{E}_n$, i.e.
    %
    \begin{equation}
        \alg{\disk (\mathsf{D}_n^*)} \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n}.
    \end{equation}
    %
    But this is just the fact that the $\disk_{\mathsf{D}_n^*}$ $\infty$-operad gives rise to $\mathbb{E}_n$-algebras from \cref{prop:framed_ndisk=En}.
\end{proof}
